\section{Test network} Used for initial testing of chaincode, available on GitHub \footnote{https://github.com/hyperledger/fabric-samples/tree/main/test-network} \label{appendix:testnet}

\section{Fabric version}
Version 2.3.2 of Fabric is, at the time of writing, the latest release, bringing many improvements which are detailed in the release notes. \footnote{https://github.com/hyperledger/fabric/releases/tag/v2.3.2} \label{appendix:version}

\section{Test Application} 
Used for initial testing and development of chaincode to application communication and vice versa, available on GitHub. \footnote{https://github.com/hyperledger/fabric-samples/tree/main/test-application} \label{appendix:testapp}
\subsection{Utils}
Provided with the test application, two utility files: \lstinline{AppUtil.js} and \lstinline{CAUtil.js} have been used in the application to handle building connection profiles, wallets, CA clients and the functionality that goes with the clients; enrolling admins and registering as well as enrolling users. \footnote{https://github.com/hyperledger/fabric-samples/tree/main/test-application/javascript} \label{appendix:utils}

\section{fabric-network Node.js SDK}
A package that encapsulates the APIs required when connecting to a Fabric network, submitting transactions, performing queries against the ledger, and listening for or replaying events. \footnote{https://www.npmjs.com/package/fabric-network} \label{appendix:nodesdk}

\subsubsection{fabric-network.Wallets}
A factory for creating wallets backed by default store implementations. \footnote{https://hyperledger.github.io/fabric-sdk-node/release-2.2/module-fabric-network.Wallets.html} \label{appendix:fabnetwallets}

\subsubsection{fabric-network.Gateway}
A package that manages network interactions on behalf of an application. A connection profile is provided as a parameter, in this case as a label matching an identity within the wallet supplied as an option \ref{appendix:fabnetwallet}. \footnote{https://hyperledger.github.io/fabric-sdk-node/release-2.2/module-fabric-network.Gateway.html} \label{appendix:fabnetgate}

\subsubsection{fabric-network.Wallet}
A package to store information for use when connecting to a Gateway. The wallet utilises a store which handles persisitence of identity information. \ref{appendix:fabnetwalletstore}\footnote{https://hyperledger.github.io/fabric-sdk-node/release-2.2/module-fabric-network.Wallet.html} \label{appendix:fabnetwallet}

\subsubsection{fabric-network.WalletStore}
Interface for store implementations that provide backing storage for identities in a Wallet. \footnote{https://hyperledger.github.io/fabric-sdk-node/release-2.2/module-fabric-network.WalletStore.html} \label{appendix:fabnetwalletstore}

\section{Node.js fabric-ca-client}
A package that encapsulates the APIs to interact with the Fabric CA. Used to manage the certificates lifecycle of registering, enrolling, renewing and revoking. \footnote{https://www.npmjs.com/package/fabric-ca-client} \label{appendix:nodeca}

\section{Node.js fabric-common}
A package that encapsulates common code used by the 'fabric-ca-client' and 'fabric-network' packages. \footnote{https://www.npmjs.com/package/fabric-common} \label{appendix:fabcommon}

\section{Node.js fabric-protos}
A package that encapsulates the Protocol Buffer files and generated JavaScript classes for Fabric. \footnote{https://www.npmjs.com/package/fabric-protos} \label{appendix:fabprotos}

\section{Fabric's Performance Traffic Engine - PTE}
A tool that uses SDKs to interact with Fabric networks by sending requests and receiving responses to see how a network performs. \footnote{https://github.com/hyperledger/fabric-test/tree/main/tools/PTE} \label{appendix:pte}

\section{Configtx.yaml}
Configuration for the network, adapted from the sample provided in the documentation for Hyperledger Fabric. \footnote{https://github.com/hyperledger/fabric-samples/blob/main/test-network/configtx/configtx.yaml} \label{appendix:configtx}

\begin{lstlisting}

\end{lstlisting}